\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{amsmath, amsthm, amssymb}
\usepackage{multicol}
\usepackage{svg}
\usepackage{caption}
\usepackage{vmargin}
\usepackage[hidelinks]{hyperref}
\usepackage[utf8]{inputenc}
 \usepackage{epigraph}

\theoremstyle{definition}
\newtheorem{defi}{Definition}[section]
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{lemma}{Lemma}[section]

\title{Series Convergence Test}
\author{Xiaozhe Yao\footnote{https://yaonotes.org/lecture-notes}}
\date{31 Jan 2020}
\begin{document}

\maketitle

\section{Fundamental Test Methods}
\begin{itemize}
    \item \textbf{$N-$th term test}: If $\lim_{n\to\infty}u_n\neq 0$, then the series is divergent.
    \item \textbf{$P-$series test}: When $p>1$, the series $\sum_{n=1}^{\infty}\frac{1}{n^p}$ is convergent; When $p\leq 1$, the $p-$ series $\sum_{n=1}^{\infty}\frac{1}{n^p}$ is divergent.
    \item \textbf{Geometric Series Test}: When $|q|<1$, the geometric series $\sum_{n=0}^{\infty}aq^{n}$ converges to $\frac{a}{1-q}$; When $|q|\geq 1$, the geometric series $\sum_{n=0}^{\infty}aq^{n}$ diverges.
    \item \textbf{Ratio Test} If $\sum_{n=1}^{\infty}u_n$ is a positive series (each entry is positive), and $\lim_{n\to\infty}\frac{u_{n+1}}{u_n}=\rho$. Then if $\rho<1$, it converges. If $\rho>1$, it diverges. When $\rho=1$, we cannot judge, and have to use other methods.
    \item \textbf{Comparison Test} Let $\sum_{n=1}^{\infty}u_n$ and $\sum_{n=1}^{\infty}v_n$ two positive series, and $u_n\leq v_n$, then if $\sum_{n=1}^{\infty}v_n$ converges, $\sum_{n=1}^{\infty}u_n$ converges as well. If $\sum_{n=1}^{\infty}u_n$ diverges, $\sum_{n=1}^{\infty}v_n$ diverges as well.
    \item \textbf{Limit Comparison Test} Let $\sum_{n=1}^{\infty}u_n$ and $\sum_{n=1}^{\infty}v_n$ two positive series, if $\lim_{n\to\infty}\frac{u_n}{v_n}=l$, then:
    \begin{itemize}
        \item If $0<l<+\infty$, they have the same convergence property, i.e. both converges or both diverges.
        \item If $l=0$, If $\sum_{n=1}^{\infty}v_n$ converges, then $\sum_{n=1}^{\infty}u_n$ converges.
        \item If $l=+\infty$, if $\sum_{n=1}^{\infty}u_n$ diverges, then $\sum_{n=1}^{\infty}u_n$ diverges.
    \end{itemize}
    \item \textbf{Alternating Series Test} If the alternating series $\sum_{n=1}^{\infty}(-1)^{n-1}u_n$ satisies: 1) $u_n>u_{n+1}$, i.e. it is monotonically decreasing. 2) $\lim_{n\to\infty}u_n=0$. Then the series converges.
\end{itemize}

\end{document}